\chapter*{\vspace{-30mm}Acknowledgements}

This thesis is made possible by the mentoring and wise advice of \textbf{Prof. Josef van Genabith} and \textbf{Dr. Francis Bond}. I thank them for their patience and the impartation of their knowledge of the machine translation and natural language processing. \textbf{Prof. Josef van Genabith} especially deserves thanks for creating various opportunities to further my knowledge on machine translation and deep/machine learning that forms the foundations of this thesis. I am also thankful for \textbf{Prof. Elke Teich} constant encouragements to my academic pursuit and her support in various side computational linguistics side projects during my stay in Saarland. 

The PhD journey couldn't have been interesting without the collaboration and beer momements with my fellow Saarland colleagues, \textit{Jon Dehdari, Jose Manuel Martinez Martinez, Noam Ordan, Santanu Pal, Anne Schumann, Mihaela Vela} and \textit{Marcos Zampieri}. I am thankful also for the fun times with my fellow EXPERT partners for going through the journey together, esp. \textit{Rohit Gupta} and \textit{Carolina Scarton}, who had joined me in several shared task participations. 

The EXPERT consortium have provided opportunities to collaborate across borders and the exchanges I have spent at WordFast, Universida de Malaga and University of Wolverhampton. My interactions with \textbf{Prof. Gloria Corpas Pastor}, \textit{Hernani Costa} and \textit{Anna Zaretskaya} at the University of Malaga gave me a better understanding of human-centric language technologies. It was an honor to work with \textbf{Mr. Yves Champollion }who had hosted me at WordFast. The experience had gave me valuable insights to the translation industry. Thank you \textbf{Prof. Ruslan, Dr. Constantin Orasan} and \textbf{Iain Mansell} for organizing the consortium and hosting me in UoW for the exchange; nothing sums up my stay at the Wolves better than the blogpost.\footnote{\url{http://rgcl.wlv.ac.uk/2016/01/26/farewell-from-liling/}}

The research leading to this thesis has received funding from the People Programme (Marie Curie Actions) of the European Union's Seventh Framework Programme FP7/2007-2013/ under REA grant agreement no. 317471.
