\iffalse
\newpage
\section{List of Publications}

{\small
Liling Tan, Carol Scarton, Lucia Specia and Josef van Genabith. 2016. SAARSHEFF: Semantic Textual Similarity with Machine Translation Evaluation Metrics Ensembles. In \textit{Proceedings of Tenth International Workshop on Semantic Evaluation (SemEval 2016}). San Diego, USA. 

Hanna Bechara, Rohit Gupta, Liling Tan, Constantin Orasan, Ruslan Mitkov and Josef van Genabith. 2016. WOLVESAAR: Replicating the Success of Monolingual Word Alignment and Neural Embeddings for Semantic Textual Similarity. In \textit{Proceedings of Tenth International Workshop on Semantic Evaluation (SemEval 2016)}. San Diego, USA. 

Jose M.M. Martinez and Liling Tan. 2016. Complex Word Identification with Sense Entropy and Sentence Perplexity. In \textit{Proceedings of Tenth International Workshop on Semantic Evaluation (SemEval 2016)}. San Diego, USA.   

Marcos Zampieri, Shervin Malmasi, Liling Tan and Josef van Genabith. 2016. MacSaar: Zipfian and Character-level features for Complex Word Identification. In \textit{Proceedings of Tenth International Workshop on Semantic Evaluation (SemEval 2016)}. San Diego, USA.   

Liling Tan, Francis Bond and Josef van Genabith. 2016. Hyponym Endocentricity. In\textit{ Proceedings of Tenth International Workshop on Semantic Evaluation (SemEval 2016)}. San Diego, USA.   

Jon Dehdari, Liling Tan and Josef van Genabith. 2016. BIRA: Improved Predictive Exchange Word Clustering. In P\textit{roceedings of the 2016 Conference of the North American Chapter of the Association for Computational Linguistics: Human Language Technologies}. San Diego, California  

Jon Dehdari, Liling Tan and Josef van Genabith. 2016. Scaling Up Word Clustering. In \textit{Proceedings of the 2016 Conference of the North American Chapter of the Association for Computational Linguistics: Demonstrations}. San Diego, California   

Liling Tan, Jon Dehdari and Josef van Genabith. 2015. An Awkward Disparity between BLEU / RIBES and Human Judgements in Machine Translation. In \textit{Proceedings of the 2nd Workshop on Asian Translation (WAT2015)}. Kyoto, Japan.  

Carolina Scarton, Liling Tan and Lucia Specia. 2015. USHEF and USAAR-USHEF Participation in the WMT15 Quality Estimation Shared Task. In \textit{Proceedings of Tenth Workshop on Statistical Machine Translation (WMT15)}. Lisbon, Portugal.  

Mihaela Vela and Liling Tan. 2015. Predicting Machine Translation Adequacy with Document Embeddings. In \textit{Proceedings of Tenth Workshop on Statistical Machine Translation (WMT15)}. Lisbon, Portugal.  

Marcos Zampieri, Liling Tan, Nikola Ljubešic, Jörg Tiedemann, Preslav Nakov. 2015. Overview of the DSL Shared Task 2015. In \textit{Proceedings of the Joint Workshop on Language Technology for Closely Related Languages, Varieties and Dialects (LT4VarDial)}. Hissar, Bulgaria  

Liling Tan, Josef van Genabith and Francis Bond. 2015. Passive and Pervasive Use of a Bilingual Dictionary in Statistical Machine Translations. In \textit{Proceedings of the Fourth Workshop on Hybrid Approaches to Translation (HyTra)}. Beijing, China. 

Liling Tan, Carol Scarton, Lucia Specia and Josef van Genabith. 2015. USAAR-SHEFFIELD: Semantic Textual Similarity with Deep Regression and Machine Translation Evaluation Metrics. In \textit{Proceedings of Ninth International Workshop on Semantic Evaluation (SemEval 2015)}. Denver, USA.  

Liling Tan, Rohit Gupta and Josef van Genabith. 2015. USAAR-WLV: Hypernym Generation with Deep Neural Nets. In \textit{Proceedings of Ninth International Workshop on Semantic Evaluation (SemEval 2015)}. Denver, USA.  

Liling Tan and Noam Ordan. 2015. USAAR-CHRONOS: Crawling the Web for Temporal Annotations. In \textit{Proceedings of Ninth International Workshop on Semantic Evaluation (SemEval 2015)}. Denver, USA.  

Liling Tan. 2015. Statistical Machine Translation with NLTK. Poster presented at \textit{Python Conference (PyCon 2015)}.

Liling Tan and Francis Bond. 2014. NTU-MC Toolkit: Annotating a Linguistically Diverse Corpus. In Proceedings of 25th International Conference on Computational Linguistics (COLING 2014). Dublin, Ireland.  

Marcos Zampieri, Liling Tan, Nikola Ljubešić, Jörg Tiedemann. 2014. A Report on the Discriminating between Similar Languages (DSL) Shared Task 2014. In \textit{Proceedings of the 1st Workshop on Applying NLP Tools to Similar Languages, Varieties and Dialects (VarDial)}. Dublin, Ireland.  

Liling Tan, Anne Schumann, Jose M.M. Martinez and Francis Bond. 2014.Sensible: L2 Translation Assistance by Emulating the Manual Post-Editing Process. In \textit{Proceedings of the Eighth International Workshop on Semantic Evaluation (SemEval 2014)}. Dublin, Ireland.  

Liling Tan and Santanu Pal. 2014. Manawi: using multi-word expressions and named entities to improve machine translation. In \textit{Proceedings of Ninth Workshop on Statistical Machine Translation (WMT14)}. Baltimore, USA.  

Guy Emerson, Liling Tan, Susanne Fertmann, Alexis Palmer and Michaela Regneri . 2014. SeedLing: Building and using a seed corpus for the Human Language Project. In \textit{Proceedings of The use of Computational methods in the study of Endangered Languages (ComputEL) Workshop}. Baltimore, USA.  

Liling Tan, Marcos Zampieri, Nikola Ljubešic, Jörg Tiedemann. 2014. Merging Comparable Data Sources for the Discrimination of Similar Languages: The DSL Corpus Collection. In \textit{Proceedings of the 7th Workshop on Building and Using Comparable Corpora (BUCC): Building Resources for Machine Translation Research}. Reykjavik, Iceland.

Constance Wang and Liling Tan. 2014.Explicit Holmes: A Diachronic Investigation of Explicitness and Explicitation in Chinese Translations of Detective Stories In Kerstin Kunz, Elke Teich, Silvia Hansen-Schirra, Stella Neumann and Peggy Daut (eds.), \textit{Caught in the Middle - Language Use and Translation: A Festschrift for Erich Steiner on the Occasion of his 60th Birthday}. page 417-428. Saarland University Press. 

}
\fi